\documentclass[12pt]{article}
\usepackage[margin=1.2in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{standalone}


\title{Group Assignment}


\begin{document}

\maketitle

\input{Introduction}

\input{Biology}

\input{Model}

\input{Simulation}

\input{Discussion}

\begin{thebibliography}{}
	\bibitem{Mesenchymal Stem Cells}
	Caplan, A. I. (1991). Mesenchymal stem cells. \textit{Journal of orthopaedic research, 9}(5), 641-650.
	\bibitem{Morphogen Gradients}
	Christian, J. L. (2012). Morphogen gradients in Development: from form to function. \textit{Wiley Interdisciplinary Reviews: Developmental Biology 1}(1):3-15.
	\bibitem{Garfinkel 2004}
	Garfinkel, A., Tintut, Y., Petrasek, D., Boström, K., \& Demer, L. L. (2004). Pattern formation by vascular mesenchymal cells. \textit{Proceedings of the national academy of sciences of the United States of America, 101}(25), 9247-9250.
	\bibitem{Garfinkel 2008}
	Yochelis, A., Tintut, Y., Demer, L. L., \& Garfinkel, A. (2008). The formation of labyrinths, spots and stripe patterns in a biochemical approach to cardiovascular calcification. \textit{New Journal of Physics, 10}(5), 055002.
	\bibitem{Lax 1956}
	Lax, P. D., \& Richtmyer, R. D. (1956). Survey of the stability of linear finite difference equations. \textit/{Communications on pure and applied mathematics, 9}(2), 267-293.
	\bibitem{Turing 1952}
	Turing, A. M. (1952). The chemical basis of morphogenesis. \textit{Philosophical Transactions of the Royal Society of London. Series B, Biological Sciences, 237}(641), 37-72.
	\bibitem{Keller Segel 1970}
	Keller, E. F., \& Segel, L. A. (1970). Initiation of slime mold aggregation viewed as an instability. \textit{Journal of Theoretical Biology, 26}(3), 399-415.
	\bibitem{Gierer Meinhardt 1972}
	Gierer, A., \& Meinhardt, H. (1972). A theory of biological pattern formation. \textit{Kybernetik, 12}(1), 30-39.
	

\end{thebibliography}
\end{document}
